Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-04 paper/main.tex
TELA automata

TELA have attracted a lot of attention during the last five years.
Their popularity comes probably from the fact that these automata can
often use less states than equivalent automata with simpler acceptance
conditions. Further, algorithms handling TELA can automatically handle
all automata with traditional acceptance conditions. TELA automata can
be obtained for example by translating LTL formulas by
Delag~\cite{muller.17.gandalf}, ltl3tela~\cite{major.19.atva},
Rabinizer~4~\cite{kretinsky.18.cav}, or
Spot~\cite{duret.16.atva2}. There are also some algorithms processing
these automata, for example the emptiness check~\cite{baier.19.atva}
or translation of TELA to parity
automata~\cite{renkin.20.atva,casares.22.tacas}.

>>>>

TELA have attracted a lot of attention during the last five years.
Their popularity comes probably from the fact that these automata can
often use less states than equivalent automata with simpler acceptance
conditions. Further, algorithms handling TELA can automatically handle
all automata with traditional acceptance conditions. TELA can
be obtained for example by translating LTL formulas by
Delag~\cite{muller.17.gandalf}, ltl3tela~\cite{major.19.atva},
Rabinizer~4~\cite{kretinsky.18.cav}, or
Spot~\cite{duret.16.atva2}. There are also some algorithms processing
these automata, for example the emptiness check~\cite{baier.19.atva}
or translation of TELA to parity
automata~\cite{renkin.20.atva,casares.22.tacas}.
